---
output: github_document
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# parn88: Parncutt's (1988) root-finding algorithm

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pmcharrison/parn88?branch=master&svg=true)](https://ci.appveyor.com/project/pmcharrison/parn88)
[![Travis build status](https://travis-ci.org/pmcharrison/parn88.svg?branch=master)](https://travis-ci.org/pmcharrison/parn88)
[![Coverage status](https://coveralls.io/repos/github/pmcharrison/parn88/badge.svg)](https://coveralls.io/r/pmcharrison/parn88?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

This R package, `parn88`, implements the
psychoacoustic root-finding algorithm of @Parncutt1988.

## Installation

You can install the package directly from Github.

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("pmcharrison/parn88")
```

## Example usage

Load the package:

``` {r}
library(parn88)
```

Analyse a chord:

```{r}
parn88(c(0, 4, 7))
```

The input is a pitch class set. There are three outputs:

- `root` - the pitch class of the estimated chord root.
- `root_ambiguity` - the ambiguity of the chord root. Ambiguity is positively
associated with dissonance.
- `pc_weight` - a 12-dimensional vector describing the weight of each pitch class.
High weight means that a pitch class is more likely to become the chord root.

It is also possible to compute chord roots and root ambiguities directly.

Chord roots:

```{r}
root(c(0, 4, 7)) # C major chord
root(c(0, 3, 7)) # C minor chord
root(c(0, 4, 9)) # A minor chord
root(c(2, 5, 7, 11)) # G7 chord
```

Root ambiguities:

```{r}
root_ambiguity(c(0, 4, 7)) # major triad
root_ambiguity(c(0, 3, 7)) # minor triad
root_ambiguity(c(0, 4, 8)) # augmented triad
root_ambiguity(c(0, 3, 6)) # dimimished triad
```

# References
